---
title: "Session 4"
description: |
  Data preparation and how to go from Luminex machine to [`covidClassifyR`](https://shaziaruybal.shinyapps.io/covidclassifyr) Shiny app
author: 
- name: Shazia Ruybal-Pesántez, PhD
  url: https://shaziaruybal.com
  affiliation: Walter & Eliza Hall Institute/Burnet Institute, Australia
  affiliation_url: https://www.burnet.edu.au/people/701_shazia_ruybal
date: 2022-03-11
output:
  distill::distill_article:
    self_contained: false
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```
### Description:
In this session you will go over how to prepare your data and upload your data to the [`covidClassifyR`](https://shaziaruybal.shinyapps.io/covidclassifyr) app, and how to check the Luminex run info, raw data file and user-supplied plate layout

### <i class="fas fa-calendar-alt"></i> Session details:
11th March 2022, 08:30-09:00am GMT+10

### <i class="fas fa-book-open"></i> Materials:
```{r icon-links}
# [TODO]: css styling for .icon-link and .icon-link:hover
icon_link(icon = "fas fa-file-pdf",
          text = "Slides",
          url = "")

icon_link(icon = "fas fa-play-circle",
          text = "Recording",
          url = "")
```

# Acknowledgments {.appendix}

This workshop was designed for Papua New Guinea Institute for Medical Research researchers and led by Dr. Shazia Ruybal-Pesántez, Dr. Maria Ome-Kaius and Dr. Fiona Angrisano. 

Funding for this workshop was provided by a [Regional Collaborations Programme COVID-19 Digital Grant](https://www.science.org.au/news-and-events/news-and-media-releases/regional-research-set-get-digital-boost) from the Australian Academy of Science and Australian Department of Industry, Science, Energy and Resources. 