---
title: "Session 1"
description: |
  Introduction to the SARS-CoV-2 Luminex multi-antigen serology assay
author: 
- name: Fiona Angrisano, PhD
  affiliation: Burnet Institute, Australia
  affiliation_url: https://www.burnet.edu.au/people/697_fiona_angrisano
date: 2022-03-10
output:
  distill::distill_article:
    self_contained: false
categories:
  - "Day 1"
citation: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```
### Description:
In this session you will go over the theory of the multi-antigen Luminex assay and tips on how to set up your assay in the lab.

### <i class="fas fa-calendar-alt"></i> Session details:
10th March 2022, 8:30-09:00am GMT+10

### <i class="fas fa-book-open"></i> Materials:
```{r icon-links}
# [TODO]: css styling for .icon-link and .icon-link:hover
icon_link(icon = "fas fa-file-pdf",
          text = "Slides",
          url = "session1_slides.pdf")

icon_link(icon = "fas fa-play-circle",
          text = "Recording",
          url = "session1_recording.mp4")
```
  
<a href="sessions/2022-03-10-session2/index.html" class="btn btn-secondary" style="float: right;">Next session <i class="fas fa-chevron-circle-right"style="color:#93c54b"></i></a>  

# Acknowledgments {.appendix}

This workshop was designed for Papua New Guinea Institute for Medical Research researchers and led by Dr. Shazia Ruybal-Pesántez, Dr. Maria Ome-Kaius and Dr. Fiona Angrisano. 

Funding for this workshop was provided by a [Regional Collaborations Programme COVID-19 Digital Grant](https://www.science.org.au/news-and-events/news-and-media-releases/regional-research-set-get-digital-boost) from the Australian Academy of Science and Australian Department of Industry, Science, Energy and Resources. 