---
title: "Session 6"
description: |
  Download your quality control report and processed data
author: 
- name: Shazia Ruybal-Pesántez, PhD
  url: https://shaziaruybal.com
  affiliation: Walter & Eliza Hall Institute/Burnet Institute, Australia
  affiliation_url: https://www.burnet.edu.au/people/701_shazia_ruybal
date: 2022-03-11
output:
  distill::distill_article:
    self_contained: false
citation: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```

### Description:
In this session you will go over how to download your processed data and quality control report and how to interpret them. 

### <i class="fas fa-calendar-alt"></i> Session details:
11th March 2022, 09:30-10:00-am GMT+10

### <i class="fas fa-book-open"></i> Materials:
```{r icon-links}
# [TODO]: css styling for .icon-link and .icon-link:hover
icon_link(icon = "fas fa-file-pdf",
          text = "Slides",
          url = "https://shaziaruybal.github.io/covidClassifyR-workshop/slides/session6/session6_slides.html")

icon_link(icon = "fas fa-play-circle",
          text = "Recording",
          url = "https://youtu.be/qCXLwPhXbA8")
```

# Acknowledgments {.appendix}

This workshop was designed for Papua New Guinea Institute for Medical Research researchers and led by Dr. Shazia Ruybal-Pesántez, Dr. Maria Ome-Kaius and Dr. Fiona Angrisano. 

Funding for this workshop was provided by a [Regional Collaborations Programme COVID-19 Digital Grant](https://www.science.org.au/news-and-events/news-and-media-releases/regional-research-set-get-digital-boost) from the Australian Academy of Science and Australian Department of Industry, Science, Energy and Resources. 