---
title: "Session 2"
description: |
  Introduction to the COVID-19 serological surveys that have been conducted in PNG
author: 
  - name: Maria Ome-Kaius, MD PhD
    affiliation: Papua New Guinea Institute of Medical Research, PNG
    affiliation_url: https://www.pngimr.org.pg
date: 2022-03-10
output:
  distill::distill_article:
    self_contained: false
categories:
  - day1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries}
library(distilltools)
```
### Description:
In this session you will be introduced to the purpose of serosurveillance research and programs and will go over the COVID-19 serological surveys that have been conducted in PNG.

### <i class="fas fa-calendar-alt"></i> Session details:
10th March 2022, 09:00-09:30am GMT+10

### <i class="fas fa-book-open"></i> Materials:

*Note: this session includes unpublished data, so to maintain confidentiality the materials will be provided to participants directly.*

# Acknowledgments {.appendix}

This workshop was designed for Papua New Guinea Institute for Medical Research researchers and led by Dr. Shazia Ruybal-Pesántez, Dr. Maria Ome-Kaius and Dr. Fiona Angrisano. 

Funding for this workshop was provided by a [Regional Collaborations Programme COVID-19 Digital Grant](https://www.science.org.au/news-and-events/news-and-media-releases/regional-research-set-get-digital-boost) from the Australian Academy of Science and Australian Department of Industry, Science, Energy and Resources. 